Bucket-Sorted Independent Sets for Algebraic Multigrid

### 2007-10-01 bsis_paper/paper.tex
Small change to one proof.
git-svn-id: file:///home/rblake/svn/pamg/trunk@32 c7f3fe13-8c30-0410-9127-9a9c42fe009c
Additional changes to proof.
git-svn-id: file:///home/rblake/svn/pamg/trunk@33 c7f3fe13-8c30-0410-9127-9a9c42fe009c

\begin{thm}
\label{5:theorem:invariance}
All independent set-based coarse-grid selection algorithms given the
same initial weights and using the same selection neighborhood,
selection criterion based on~(\ref{eqn:general-selection}), and weight
update heuristics as described above select identical coarse grids.
\end{thm}
\begin{proof}
Let $c$ be the vertices in the extended selection neighborhood of $i$
($\mathcal{N}_i^{2s}$) satisfying the conditions for $D$ in some
arbitrary iteration. Suppose assigning vertices $c_1 \subset c$ to the
$C$-point set leads to $w_i > w_j$ for all $j \in
\mathcal{N}_i^s$. Also suppose assigning $c_2 \subset c$, $c_1 \ne
c_2$, to the $C$-point set leads to the existence of some $j \in
\mathcal{N}_i^s$ such that $w_j > w_k$ for all $k \in
\mathcal{N}_j^s$. In the first case, $i$ becomes a $C$-point before
$j$, and the opposite is true in the second case.

>>>>

\begin{thm}
\label{5:theorem:invariance}
All independent set-based coarse-grid selection algorithms given the
same initial weights and using the same selection neighborhood,
selection criterion based on~(\ref{eqn:general-selection}), and weight
update heuristics as described above select identical coarse grids.
\end{thm}
\begin{proof}
  Let $c$ be the vertices in the extended selection neighborhood of
  $i$ (i.e., $\mathcal{N}_i^{2s}$) satisfying the conditions for $D$
  in some arbitrary iteration, where $i \notin c$. Suppose assigning
  vertices $c_1 \subset c$ to the $C$-point set leads to $w_i > w_j$
  for all $j \in \mathcal{N}_i^s$. Additionally, suppose assigning
  $c_2 \subset c$, $c_1 \ne c_2$, to the $C$-point set leads to $w_j >
  w_k$ for all $k \in \mathcal{N}_j^s$ for some $j \in
  \mathcal{N}_i^s$, $j \notin c$. In the first case, $i$ becomes a
  $C$-point before $j$, and the opposite is true in the second case.
